### 2016-11-04 paper/evaluation.tex
pass on eval

\newcommand{\RQB}{What is the distribution of CPU and IO bound
regression tests from the sample set?}
\newcommand{\RQC}{How the execution time is distributed among test
cases?}
\newcommand{\RQD}{How often developers use the parallelism features
from build manager systems to improve performance on test execution?}

@@

The first research question addresses the distribution of subjects per
elapsed time to execute regression tests. We are interested on
identifying time-consuming test suites \Jbc{do we have a better
argument than this?}for further investigation. The
second research question addresses the distribution of execution time
per test case for each project. The rationale is that if the time cost
of a regression test is equally distributed among test cases, the
execution cost could be potentially improved by running tests in
parallel (in contrast to the scenario where only one test case
dominates most of the execution time).

@@

To evaluate the frequency of time-consuming regression tests, we
considered \Fix{X} Maven and \Fix{Y} Ant projects (\Fix{X+Y} total)
that we were able to run the tests. For each subject, we first
compiled the source and later, tested and collected the elapsed time
reported from the build system using regular expressions. To avoid
inflating the reported time, we run the tests ignoring non-related
tasks (\eg, \emph{javadoc} generation). In case of \emph{Maven}
projects, use \Jbc{How to show the following command?} \Fix{mvn test
-Dmaven.javadoc.skip=true}; in contrast, for \emph{Ant} projects, we
used \Fix{ant test} and manually inspected the test execution to
ignore any non-related tasks, if any.

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}). Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group. It is important to mention that
Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
time: some tests may finish early due to a failure since the subjects
were tested in a potentially unstable revision. \Fix{Results indicate
that a relatively high number of projects...}.

@@

For the subjects from the groups \emph{medium} and \emph{long}, we
compared the execution time and the number of tests successfully
executed. As expected, Figure~\ref{fig:scatters} reveals that the
number of tests cases are not related to the elapsed time.
\Fix{explain briefly what dominates a test execution/types of tests}.
We ignored outliers for better visualization.

>>>>

\newcommand{\RQB}{What is the distribution of CPU and IO bound
regression tests from the sample set?}

\newcommand{\RQC}{How uniformly distributed is the execution time
across test cases in costly projects?}

\newcommand{\RQD}{How often developers use the parallelism features
from build manager systems to improve performance on test execution?}

@@

The first research question addresses the distribution of subjects per
time cost. We are interested on identifying time-consuming test suites
to investigate further their characteristics (\eg, type of application
and bottlenecks from execution) \Jbc{do we have a better arguments?}.
The second research question addresses the distribution of execution
time per test case. For each subject identified in the first research
question, we are interested in understanding how balanced is the cost
of the test suite in contrast to the cost of test cases and if there
are subjects where the time cost is mostly dominated by a small
fraction of test cases.

\Comment{The rationale is that if the time cost
of a regression test is equally distributed among test cases, the
execution cost could be potentially improved by running tests in
parallel (in contrast to the scenario where only one test case
dominates most of the execution time).}

@@

To evaluate the frequency of time-consuming regression tests, we
considered \Fix{X} Maven and \Fix{Y} Ant projects (\Fix{X+Y} total)
that we were able to test. For each subject, we first compiled the
source files and later, we ran the tests and used regular expressions
to collect the elapsed time reported from the build system. To avoid
inflating the time cost from test execution, we ignored non-related
tasks (\eg, \emph{javadoc} generation). \Fix{elaborate: In case of
\emph{Maven} projects, we use \Jbc{How to show the following command?}
\Fix{mvn test -Dmaven.javadoc.skip=true}; in contrast, for \emph{Ant}
projects, we used \Fix{ant test} and manually inspected the test
execution to ignore any non-related tasks, if any}.

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}). Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group. It is important to mention that
Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
time: some tests may finish early due to a failure since the subjects
were tested in a potentially unstable revision. Results indicate
that a relatively high number of projects from the sample set requires
at least five minutes to execute. The longest execution takes \Fix{x}
to finish.

@@

Considering the groups \emph{medium} and \emph{long}, we investigated
the relation between number of tests cases and time cost from
subjects.  \Fix{elaborate: As expected, Figure~\ref{fig:scatters}
reveals that the number of tests cases are not related to the elapsed
time.  \Fix{explain briefly what dominates a test execution/types of
tests}.  We ignored outliers for better visualization.} Results
indicate that \Fix{...conclusion...}.
